---
title: "Statistical_Inference"
author: "Laura Bennett"
date: "June 29, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistical Inference for Data Science: Chapter 7 Exercises

1. I simulate 1,000,000 standard normals. The LLN says that their sample average must be close to?
  + **As they are standard normals, each will have an average of $\mu = 0$; the LLN states that their sample average must then be equal to 0 as well.**
  
2. About what is the probability of getting 45 or fewer heads out of 100 flips of a **fair coin**? (Use the CLT, not the exact binomial calculation)
  + **According to the CLT, as you collect more sample averages, the distribution you are measuring will eventually converge to a normal distribution. In this case, the distribution will have a mean of $\mu = 50$; the standard deviation of the coin was originally $\sqrt{np\left(1-p \right )}=\sqrt{100\cdot 0.5\left(0.5 \right )}=5$ as per the calculation for a binomial distribution, but the standard deviation for the assumed normal distribution will be $\frac{\sigma}{\sqrt{n}}=\frac{5}{\sqrt{100}}=0.5$. Now, using a normal distribution, we can calculate the probability of getting 45 or fewer heads:**
  ```{r,eval=TRUE}
  pnorm(45, mean=50, sd=0.5, lower.tail=TRUE)
  ```
  
3. Consider the father.son data. Using the CLT and assuming that the fathers are a random sample from a population of interest, what is a 95% confidence mean height in inches?
  + **The 95% confidence interval for a normal distribution may be calculated as $\bar X\pm \frac{2\sigma}{\sqrt{n}}$. Thus, we may calculate the confidence interval for this dataset as:**
  ```{r,eval=TRUE}
  library(UsingR)
  data(father.son)
  xbar <- mean(father.son[['fheight']])
  sd <- sd(father.son[['fheight']])
  n <- length(father.son[['fheight']])
  upper <- (xbar + (2*sd)/sqrt(n))
  lower <- (xbar - (2*sd)/sqrt(n))
  print(paste('(',lower,',',upper,')'))
  ```
  

4. The goal of a confidence interval having coverage 95% is to imply what?
  + **The probability that the sample mean is in the interval is 95%**
  
5. The rate of search entries into a web site was 10 per minute when monitoring for an hour. Use R to calculate the exact Poisson interval for the rate of events per minute.
  +  **We may use the r function poisson.test() to calculate the exact Poisson interval:**
  ```{r,eval=TRUE}
  poisson.test(600,T=60)
  ```
  
6. Consider a uniform distribution. If we were to sample 100 draws from a uniform distribution (which has a mean of 0.5 and a variance of 1/12) and take their mean $\bar{X}$, what is the approximate probability of getting as large as 0.51 or larger?
  + **This is similar to problem #2, as we are modeling a uniform distribution with a normal distribution with mean $\mu = 0.5$ and standard deviation $\sigma = \sqrt\frac{\sigma^2}{n}=\sqrt{\frac{\frac{1}{12}}{100}}$**
  ```{r,eval=TRUE}
  sd <- sqrt((1/12)/100)
  pnorm(0.51,0.5,sd,lower.tail = FALSE)
  ```