---
title: "Statistical_Inference"
author: "Laura Bennett"
date: "July 13, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistical Inference for Data Science: Chapter 9 Exercises

1. Which hypothesis is typically assumed to be true in hypothesis testing?
  + **The null hypothesis**
  
2. The type I error rate controls what?
  + **The probability that the null hypothesis will be incorrectly rejected.**
  
3. Load the dataset mtcars in the datasets R package. Assume that the data set mtcars is a random sample. Compute the mean MPG, $\bar{x}$, of this sample. You want to test whether the true MPG is $\mu _0$ or smaller using a one-sided 5% level test ($H_0:\mu=\mu_0$ versus $H_a:\mu<\mu_0$). Using that data set and a Z test: Based on the mean MPG of the sample $\bar{x}$, and by using a Z test: what is the smallest value of $\mu _0$ that you would reject for (to two decimal places)?
  + **Remember that a z-score defines the number of standard deviations from the mean a data point is and is calculated as $Z=\frac{\bar{X}-\mu_0}{\frac{s}{\sqrt{n}}}$. We may calculate the Z-score that we want given our desired p-value (0.05); from there, we can solve the Z-score equation to calculate the value of $\mu _0$ that would serve as the cutoff for rejection of the null hypothesis (the null hypothesis being that $\mu _0$ is equal to $\bar{X}$ while the alternative is that it is smaller).**
  ```{r,eval=TRUE}
  library(datasets); data(mtcars)
  xbar <- mean(mtcars$mpg)
  z <- qnorm(0.05)
  sd <- sd(mtcars$mpg)
  n <- length(mtcars$mpg)
  cutoff <- xbar-(z*sd/sqrt(n))
  round(cutoff,digits=2)
  ```
4. Consider again the mtcars dataset. Use a two group t-test to test the hypothesis that the 4 and 6 cylinder cars have the same mpg. Use a two sided test with unequal variances. Do you reject?
  +
  ```{r,eval=TRUE}
  mpg4 <- mtcars$mpg[mtcars$cyl==4]
  mpg6 <- mtcars$mpg[mtcars$cyl==6]
  test<- t.test(mpg4,mpg6,alternative='two.sided',var.equal=FALSE,paired=FALSE,conf.level=0.95)
  round(test$p.value,digits=4)
  ```
  **Since the p-value is less than 0.05, we may reject the null hypothesis in favor of the alterantive (the two different cylinders have different average mpgs) **

5. A sample of 100 men yielded an average PSA level of 3.0 with an sd of 1.1. What are the complete set of values that a 5% two sided Z test of $H_0 : \mu = \mu_0$ would fail to reject the null hypothesis for?
  + **This requires the same method as in number 3 - however, we are solving for those values at both the upper and lower cutoffs s.t. 5% of the probability density is outside the interval. **
  ```{r,eval=TRUE}
  xbar <- 3
  sd <- 1.1
  n <- 100
  round(3+c(-1,1)*qnorm(0.975)*sd/sqrt(n),digits=2)
  ```

6. You believe the coin that you're flipping is biased towards heads. You get 55 heads out of 100 flips. Do you reject at the 5% level that the coin is fair?
  + **In order to solve this problem, we must find the probability of getting 55 heads out of 100 flips if we had a FAIR coin. We may do that using the cumulative distribution function for a binomial distribution as follows: **
  ```{r,eval=TRUE}
  xbar = 55
  n = 100
  sd = sqrt(n*0.5*(1-0.5))
  pbinom(xbar-1,size=100,prob=0.5,lower.tail = FALSE)
  ```
  
7. Suppose that in an AB test, one advertising scheme led to an average of 10 purchases per day for a sample of 100 days, while the other led to 11 purchases per day (also for a sample of 100 days). Assuming a common standard deviation of 4 purchases per day and assuming that the groups are independent and their days are iid, perform a Z test of equivalence. Do you reject at the 5% level?
  + **The Z statistic for two groups may be calculated as $Z=\frac{\bar{X_1}-\bar{X_2}-(\mu_1-\mu_2)}{s_p\sqrt{\frac{1}{n_1}+\frac{1}{n_2}}}$, where in this case $\bar{X_1}=10$, $\bar{X_2}=11$, $n_1=n_2=100$, $s_p=4$, and $(\mu_1-\mu_2)=0$ (since we are testing whether the two population means could be considered "equal," the difference between them would hypothetically be zero). Given a z-statistic, we may then calculate the probability of getting that particular statistic on a standard normal distribution; if the probability is less than 5%, then we may reject the null hypothesis and say that the two groups have statistically significant differences in their means. Thus: **
  ```{r,eval=TRUE}
  n1 <- 100; n2 <- 100
  xbar1 <- 10 ;xbar2 <- 11
  sp <- 4
  z <- (xbar1-xbar2-0)/(sp*sqrt((1/n1)+(1/n2)))
  pnorm(z)
  ```
  **Since $p\approx 0.038 < 0.05$, we may reject the null hypothesis and support the second advertising scheme with confidence. **
  
8. A confidence interval for the mean contains:
  + **All of the values of the hypothesized mean for which we would fail to reject with $\alpha = 1-Conf. Level$**
  
9. In a court of all, all things being equal, if via policy you require a lower standard of evidence ot convict people then:
  + **More innocent people will be convicted. **