---
title: "Statistical_Inference1"
author: "Laura Bennett"
date: "June 3, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistical Inference for Data Science: Chapter 5 Exercises

1. If I have a random sample from a population, the sample variance is an estimate of what?
  + **The population variance**
  
2. THe distribution of the sample variance of a random sample from a population is centered at what?
  + **The population variance**
  
3. I keep drawing samples of size $n$ from a population with variance $\sigma ^2$ and taking their average. I do this thousands of times. If I were to take the variance of the collection of averages, what would it be?
  + **In this case, you are seeking the standard error of the mean, a measure of the variability of the mean of a distribution. Thus, the variance of the collection of averages should be $\frac{\sigma ^2}{n}$**

4. You get a random sample of $n$ observations from a population and take their average. You would like to estimate the variability of averages of $n$ observations from this population to better understand how precise of an estimate it is. Do you need to repeatedly collect averages to do this?
  + **No; you may instead divide the variance by $n$ and obtain the standard error of the mean.**
  
5. A random variable takes the value -4 with probability 0.2 and 1 with probability 0.8. What is the variance of this random variable?
  +  **The variance of a random variable may be found as $Var(X)=E(X^2)-E(X)^2$, where $E(X)=\sum x_ip(x)$. In this case, $E(X)=(-4)(0.2)+(1)(0.8)=0$ and $E(X^2)=(-4)^2(0.2)+(1)^2(0.8)=4.0$; therefore, $Var(X)=4.0-0=4.0$**
  
6. If $\bar X$ anad $\bar Y$ are comprised of $n$ iid random variabls arising from distributions having means $\mu _x$ and $\mu _y$ respectively and common variance $\sigma ^2$, what is the variance $\bar X - \bar Y$?
  + **According to the central limit theorem, $Var(X\pm Y)=Var(X)+Var(Y)$ IF $X$ and $Y$ are independent. Given that the sample variance from both $X$ and $Y$ is $\frac{\sigma ^2}{n}$, $Var(\bar X- \bar Y)=\frac{2\sigma ^2}{n}$ **
  
7. Let $X$ be a random variable have a standard deviation $\sigma$. What can be said about the variance of $\frac{X}{\sigma}$?
  + **The variance of a constant times a random variable is given by $Var(aX)=a^2Var(X)$. Thus, $Var\left (\frac{X}{\sigma}  \right )= \frac{\sigma ^2}{\sigma ^2}=1$ **
  
8. What would be the variance for a random variable with values [2:5] and accompanying probabilities (0.1, 0.2, 0.3, 0.4)?
  +
    ```{r, eval=TRUE}
    p<-c(.1,.2,.3,.4)
    x<-2:5
    variance <- sum(x^2*p)-(sum(x*p))^2
    print(variance)
    ```
9. If you roll ten standard dice, take their average, then repeat this process over and over and construct a histogram, what would be its variance expressed to 3 decimal places?
  + **The variance of a standard die may be calculated as $Var(X)=\frac{1}{6}\left [ 1^2+2^2+3^2+4^2+5^2+6^2 \right ]-\frac{1}{6^2}\left[1+2+3+4+5+6 \right ]^2=2.92$. Since we are essentially looking for the variance of the mean, we may calculate it as $Var(\bar X)=\frac{\sigma ^2}{n}=\frac{2.92}{10}=0.292$ **